Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-12 rainbowCAM.tex
Going home now.

We have calculated the full spectrum of Regge poles for a compact body spacetime for the first time.

We find 2 distinct branches - - in the case $R > 3M$, and a third branch of narrow resonances appears for UCO.

Confident that there are no additional poles in the first quadrant with imaginary parts less than (blah), for two reasons. First, we have scanned across the domain using the scanning method. Second, we obtain an excellent agreement, which would not be the case if poles in this domain had been missed.

@@

Through a WKB method, we have obtained qualitative understanding of the broad resonances, finding that the imaginary part is predicted, with a certain degree of accuracy, from the discontinuity in the potential at the surface of the body. Further work is need on modelling the surface-wave branch, the narrow resonances. Taking the WKB method to higher orders will presumably improve the accuracy.

>>>>

In this work, we have calculated the full spectrum of Regge poles for a compact body spacetime for the first time; we have applied CAM theory to obtain a complementary expression for the scattering amplitude (); and we have used this expression to calculate scattering cross sections numerically, showing precise agreement with the numerical results of the partial-wave expansion first obtained in Ref.~\cite{Dolan:2017rtj}.

The spectrum of Regge poles for the neutron star case ($R/M = 6$) exhibits two distinct branches of poles (see ), which we have labelled `broad resonances' and `surface waves' \cite{}. Ultra-compact objects have, in addition, a third branch of `narrow resonances' corresponding to modes inside a cavity between the light-ring and their surface.

@@

By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~). Taking the WKB method to higher orders will presumably improve the accuracy of approximation. Further work is need to model the surface-wave branch, and the narrow-resonance branch.

We can be confident that there are no additional branches Regge poles in the first quadrant, for two reasons. First, we have searched across the complex-$\lambda$ domain using the scanning method detailed in Sec.~. Second, in our calculation of $d\sigma/d\Omega$, we find a precise numerical agreement between our CAM calculation and our partial-wave calculation; this would not be the case if poles in this domain had been missed.
